Paper 1

### 2018-09-15 paper1.tex
Finished 1st draft

\begin{abstract}
	Complete the document to make it readable by an audience of your peers.
	The source file contains some hints and ideas.
	Before submitting, please delete the begin \& end abstract tags and everything between them.
	Make sure you include your PSEUDONYM in the document.
	To submit, compile the paper, and submit the PDF file through Canvas.

	You may work with others when figuring out the proofs, but you should acknowledge your peer collaborators in a comment on the Canvas submission (do not acknowledge them in the document submitted).
	You should also acknowledge any peer tutors, books, web pages or other sources you used in a Canvas comment.
	There is no need to acknowledge the Proofs So Far, or other class materials, but you may like to refer to ``Proposition~1.9 of Proofs So Far'', etc.,\ if you are using theorems we already proved.
	{\color{red}You may \emph{not} share \LaTeX{} source files.}

	This is a challenging assignment!
	You are encouraged to interact with other students, according to the rules above, when constructing your proofs.
	It is OK to submit incomplete solutions, as partial credit is available, particularly for the most difficult proofs.
	Some theorems contain multiple statements, and there is credit available for establishing each claim of the theorem.
\end{abstract}

@@

\begin{proof}[Correct proof of theorem~\ref{thm:mean-spirited}]
	%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
	%
	% HINTS
	%
	% Use the AM-GM inequality.
	%
	\begin{comment} %My initial longer solution
		From the AM-GM inequality, we know
		\begin{align*}
		\frac{a+b+c}{3} \geq \sqrt[3]{abc}. 
		\end{align*}
		Because we know $abc$ is a positive number, $\sqrt[3]{abc}$ is also positive. So, we can perform the following,
		\begin{align*}
		\frac{(a+b+c)(\sqrt[3]{abc})^2}{3} &\geq abc \\
		\frac{(a+b+c)}{(abc)^{\frac{1}{3}}} &\geq 3 \\
		\frac{(a)^{\frac{2}{3}}}{(bc)^{\frac{1}{3}}} + \frac{(b)^{\frac{2}{3}}}{(ac)^{\frac{1}{3}}} + \frac{(c)^{\frac{2}{3}}}{(ab)^{\frac{1}{3}}}&\geq 3 \\
		\sqrt[3]{\frac{a^2}{bc}}+\sqrt[3]{\frac{b^2}{ac}}+\sqrt[3]{\frac{c^2}{ab}}&\geq 3
		\end{align*}
		We know that all terms are positive in the above inequality, so,
		$$ \frac{a^2}{bc} + \frac{b^2}{ac} + \frac{c^2}{ac} \geq \sqrt[3]{\frac{a^2}{bc}}+\sqrt[3]{\frac{b^2}{ac}}+\sqrt[3]{\frac{c^2}{ab}}\geq3.$$
		This implies that 
		$$ \frac{a^2}{bc} + \frac{b^2}{ac} + \frac{c^2}{ac} \geq 3 .$$
	\end{comment}
	%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

@@

	If $x+1$ is divisible by $n$, then $\frac{x+1}{n}\in \NNzero$ and $0\leq\frac{x+1}{n}\leq x$. Since we know that $P(k)$ is true, we know that there exists an $n$-ary sequence such that 
	$$
		\frac{x+1}{n} = \sum_{j=0}^\infty a_{\frac{x+1}{n},j} n^j
	$$
	where $a_{\frac{x+1}{n},j}$ is the $j$th term in the sequence $a_{\frac{x+1}{n}}$
	Manipulating this equation yields, 
	\begin{align*}
		x+1 &= \sum_{j=0}^\infty a_{\frac{x+1}{n},j} n^{j+1} \\
		x+1 &= \sum_{j=1}^\infty a_{\frac{x+1}{n},j-1} n^{j}.
	\end{align*}
	Now let us define a new sequence $a_{x+1}$ such that $a_{x+1,j} = a_{\frac{x+1}{n},j-1}$
	%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

>>>>

@@

\begin{proof}[Correct proof of theorem~\ref{thm:mean-spirited}]
	%%%%%%%%%%22%%%%%%%%%%%%%%%%%%%%%%%
	%
	% HINTS
	%
	% Use the AM-GM inequality.
	%
	\begin{comment} %My initial longer solution
		From the AM-GM inequality, we know
		\begin{align*}
		\frac{a+b+c}{3} \geq \sqrt[3]{abc}. 
		\end{align*}
		Because we know $abc$ is a positive number, $\sqrt[3]{abc}$ is also positive. So, we can perform the following,
		\begin{align*}
		\frac{(a+b+c)(\sqrt[3]{abc})^2}{3} &\geq abc \\
		\frac{(a+b+c)}{(abc)^{\frac{1}{3}}} &\geq 3 \\
		\frac{(a)^{\frac{2}{3}}}{(bc)^{\frac{1}{3}}} + \frac{(b)^{\frac{2}{3}}}{(ac)^{\frac{1}{3}}} + \frac{(c)^{\frac{2}{3}}}{(ab)^{\frac{1}{3}}}&\geq 3 \\
		\sqrt[3]{\frac{a^2}{bc}}+\sqrt[3]{\frac{b^2}{ac}}+\sqrt[3]{\frac{c^2}{ab}}&\geq 3
		\end{align*}
		We know that all terms are positive in the above inequality, so,
		$$ \frac{a^2}{bc} + \frac{b^2}{ac} + \frac{c^2}{ac} \geq \sqrt[3]{\frac{a^2}{bc}}+\sqrt[3]{\frac{b^2}{ac}}+\sqrt[3]{\frac{c^2}{ab}}\geq3.$$
		This implies that 
		$$ \frac{a^2}{bc} + \frac{b^2}{ac} + \frac{c^2}{ac} \geq 3 .$$
	\end{comment}
	%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

@@

	If $x+1$ is divisible by $n$, then $\frac{x+1}{n}\in \NNzero$ and $0\leq\frac{x+1}{n}\leq x$. Since we know that $P(k)$ is true, we know that there exists an $n$-ary sequence such that 
	$$
		\frac{x+1}{n} = \sum_{j=0}^\infty a_{\frac{x+1}{n},j} n^j
	$$
	where $a_{\frac{x+1}{n},j}$ is the $j$th term in the sequence $(a_{\frac{x+1}{n}})_{j\in\NN^0}$
	Manipulating this equation yields, 
	\begin{align*}
		x+1 &= \sum_{j=0}^\infty a_{\frac{x+1}{n},j} n^{j+1} \\
		x+1 &= \sum_{j=1}^\infty a_{\frac{x+1}{n},j-1} n^{j}.
	\end{align*}
	Now, let us define a new sequence $(a_{x+1,j})_{j\in\NN^0}$ such that $a_{x+1,j} = a_{\frac{x+1}{n},j-1}$ for all $j\in \NN$ and $a_{x+1,0} = 0 $. We can then rewrite the previous equation as
	\begin{align*}
		x+1 &= 0+ \sum_{j=1}^\infty a_{x+1,j} n^{j} \\
		x+1 &=  \sum_{j=0}^\infty a_{x+1,j} n^{j}.
	\end{align*}
	This new sequence is eventually zero because the original sequence $(a_{\frac{x+1}{n},j})_{j\in\NN^0}$ was eventually zero. 
	This new sequence is also $n$-ary because $(a_{\frac{x+1}{n},j})_{j\in\NN^0}$ is $n$-ary and we only added another $0$. So we have shown that $P(x+1)$ is true if $x+1$ is divisible by $n$.

	Next, consider the case where $x+1$ is not divisible by $n$. 
	Then, the quotient remainder theorem states that there exists an integer $r$, $1\leq r\leq n-1$ such that $\frac{x+1-r}{n} \in \NN$. 
	So, we can write $0\leq\frac{x+1-r}{n}\leq x$. By our inductive hypothesis, we know
	\begin{align*}
		\frac{x+1-r}{n} &= \sum_{j=0}^\infty a_{\frac{x+1-r}{n},j} n^{j} \\
		x+1-r &= \sum_{j=0}^\infty a_{\frac{x+1-r}{n},j} n^{j+1} \\
		x+1 &= r + \sum_{j=1}^\infty a_{\frac{x+1-r}{n},j-1} n^{j}.
	\end{align*}
	Now, we can define a new sequence $(a_{x+1,j})_{j\in\NN^0}$ such that $a_{x+1,j} = a_{\frac{x+1-r}{n},j-1}$ for all $j\in \NN$ and $a_{x+1,0} = r $. We can then rewrite the previous equation as
	\begin{align*}
		x+1 &= r + \sum_{j=1}^\infty a_{x+1,j} n^{j}\\
		x+1 &= \sum_{j=0}^\infty a_{x+1,j} n^{j}.
	\end{align*}
	This new sequence is eventually zero because the original sequence  $(a_{\frac{x+1-r}{n},j})_{j\in\NN^0}$ was eventually zero. This new sequence is also $n$-ary because  $(a_{\frac{x+1-r}{n},j})_{j\in\NN^0}$ is $n$-ary, and we added an additional term $r$ which is $1\leq r\leq n-1$. So we have shown that $P(x+1)$ is also true if $x+1$ is not divisible by $n$.

	Therefore $P(x+1)$ is true for all $n\geq2$. By complete induction on $x$, $P(x)$ is true, and the theorem is proved.
